---
title       : Vitamin C on Tooth Growth in Guinea Pigs
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [shiny]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Background

This shiny application allows you to predict the tooth length based on the type of Vitamin C and the dosage. A linear regression model is built on the ToothGrowth dataset. In order to predict the tooth growth, enter the dosage and select the vitamin C type in the shiny application.

--- .class #id 

## Data
The dataset used is the result of the experiment on the effect of vitamin C on tooth growth in guinea pigs. The response is the length of odontoblasts (teeth) in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1, and 2 mg) with each of two delivery methods (orange juice or ascorbic acid).


A data frame with 60 observations on 3 variables:

[,1]    len        numeric        Tooth length

[,2]	supp	factor	Supplement type (orange juice or ascorbic acid).

[,3]	dose	numeric	Dose in milligrams.
```{r, echo=FALSE}
data(ToothGrowth)
str(ToothGrowth)
```

--- .class #id 

## Model

A linear regresssion model is built on the dataset. [Click here](https://leenc.shinyapps.io/shiny/) to launch the shiny application!
```{r, echo=FALSE}
best_model<-lm(len ~ ., data=ToothGrowth)
summary(best_model)
```


